Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-01 journal/article.tex
Work in progress

>>>>

[P40]
* Why: The IT organization was to pilot new methods as parts of the company strategy
* Who: Pilot projects were identified by consultants
* Amount: 3 projects
* What: Piloting in critical projects
* Why: To identify what management tooling can be used in agile
* Result: Data showed that agile was working
* Result: There were problems in the distributed pilot project
* Result: The consultants moved out, and continuing agile became an internal matter
* Result: Pilots showed where method was not working
* Benefit: Results of pilots were used to shape the agile model
* Benefit: The pilots showcased agile in a good way, there was good word-of-mouth
* Benefit: People got interested
